PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-17 paper/sec-conclusion.tex

\section{Conclusions and Outlook}
\label{sec:conclusion}
{\bf MZ I would like to have some sort of introduction here (a short bla bla on precision), before turning to Pineappl}

We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations from an external Monte Carlo in a PDF-independent way using interpolation grids.
This offers the advantage of fast a-posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$.
Another application that we focused on is PDF fitting, where the interpolation grids constitute the theoretical input.
We tested \textsc{PineAPPL} together with \textsc{mg5\_aMC@NLO} and found a precision of \numrange{e-4}{e-5} relative to the MC result, which is more than enough for the applications described before.
Although we used \textsc{mg5\_aMC@NLO}, we note that \textsc{PineAPPL} is not tied in any way to a specific MC and can be easily interfaced with any generator.

>>>>

\section{Conclusions and Outlook}
\label{sec:conclusion}
The systematic inclusion of EW corrections in collider-physics simulations is crucial when high accuracy is required. Until
now, it was possible to include these effects only in one of the two ingredients of the physical cross section, namely
the short-distance (partonic) matrix element. For what concerns the second ingredient, PDFs, they were still extracted including
only QCD effects. In this paper, we amended to this situation, making it possible to include EW effects also in PDF fits.
We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations from an external Monte Carlo in a PDF-independent way using interpolation grids.
This offers the advantage of fast a-posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$.
Another application that we focused on is PDF fitting, where the interpolation grids constitute the theoretical input.
We tested \textsc{PineAPPL} together with \textsc{mg5\_aMC@NLO} and found a precision of \numrange{e-4}{e-5} relative to the MC result, which is more than enough for the applications described before.
Although we used \textsc{mg5\_aMC@NLO}, we note that \textsc{PineAPPL} is not tied in any way to a specific MC and can be easily interfaced with any generator.

### 2020-08-17 paper/sec-results.tex

\paragraph{Experimental measurements and process features.}
We select the single-differential transverse momentum distribution of the
sum of the two leptons (the \enquote{Z boson}), $p_\mathrm{T}^{\ell \bar{\ell}}$, measured by the CMS experiment at a
centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
This measurement, which has not been included in any PDF determination so far,
shows very low experimental uncertainties (at the percent level or below).
EW corrections are therefore expected to be essential to achieve a good
description of it, and to constrain accurately the PDFs, together with
NNLO QCD corrections, which are already well
known~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
{\bf MZ there are at least 5-6 other papers both
  by the Zurich group and the Argonne one, but on Z+jet rather than
  Z-pt predictions. Should we cite them?}
Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt},
were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in a dedicated study~\cite{Boughezal:2017nla},
in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with another LO and NLO, which are
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
EW corrections for this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis}.

>>>>

\paragraph{Experimental measurements and process features.}
We select the single-differential transverse momentum distribution of the
sum of the two leptons (the \enquote{Z boson}), $p_\mathrm{T}^{\ell \bar{\ell}}$, measured by the CMS experiment at a
centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
This measurement, which has not been included in any PDF determination so far,
shows very low experimental uncertainties (at the percent level or below).
EW corrections are therefore expected to be essential to achieve a good
description of it, and to constrain accurately the PDFs, together with
NNLO QCD corrections, which are already well
known~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt},
were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in a dedicated study~\cite{Boughezal:2017nla},
in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with another LO and NLO, which are
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
EW corrections for this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis}.
